\documentclass{article}

\usepackage[T1]{fontenc}

\usepackage[margin=1.0in]{geometry}
\usepackage{longtable}

\usepackage{amsmath}

\newcounter{example}
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   \noindent \textit{Example~\theexample. #1} \rmfamily}{\medskip}

\usepackage{bbm}
\usepackage{booktabs}

\newcommand{\fabs}[1]{\mid {#1} \mid}

\newcommand{\bet}[1]{\llbracket {#1} \rrbracket^{\beta} }
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{makecell}

% \usepackage{mathabx}
\usepackage{amssymb,forest}

\usepackage{float}
\usepackage{MnSymbol}
\newlength\q
\newlength\smallCol
\newlength\argsLen
\setlength\q{\dimexpr .5\textwidth -2\tabcolsep}
\setlength\smallCol{\dimexpr .15\textwidth}
\setlength\argsLen{\dimexpr .2\textwidth}


\newcommand{\lto}{\mathbin{\to}}
\usepackage{booktabs}
\usepackage{enumitem} 
\usepackage{array}% for extended column definitions
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{tabto}
\newcommand{\ov}[2]{\ensuremath{\overset{\cdot {#2} \cdot}{#1}}}
\newcommand{\imp}{\rightarrow}

\usepackage{xstring}
\usepackage[german]{babel}
\usepackage[utf8]{inputenc}

\usepackage{lipsum}
\usepackage{listings}

\newcommand{\tcr}[1]{\textcolor{red}{#1}}

\definecolor{palegreen}{rgb}{0.9,1,0.9}
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=palegreen,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=5pt,
    arc=0pt,outer arc=0pt,
  }

\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{lightpink}{rgb}{1.0,0.9,0.9}
\definecolor{darkblue}{rgb}{0,0,0.4}

\usepackage{hyperref}

\hypersetup{colorlinks=true,linkcolor=darkblue,citecolor=darkblue}



\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\lstset{language=Python}

\title{Gralog Console Manual}

\author{Roman
  Rabinovich\\ \texttt{roman.rabinovich@tu-berlin.de}}

\date{\today}

\begin{document}

\maketitle


\begin{abstract}
Gralog is a visual tool for working with graphs, logics, games,
transition systems and other structures based on undirected and
directed graphs. It can create, load, save and edit graphs in
various formats.

The key focus of Gralog is simplicity of use and a short time of
learning how to use it.

A special property of Gralog is that it helps the developer to write
programmes for graphs in any language capable of working with
pipes. Gralog visualises the run of the programme and can keep track
of values of user defined variables.

The interaction between Gralog and the external programme is
performed by a simple, but powerful protocol. In the first version
we implemented a library for Python that simplifies the interaction
and abstracts away the use of pipes. This paper describes the
protocol and the library, the External Programming Module (EPM). This
includes documentation of methods and classes pertaining to the
EPM and code examples for how to use these.
\end{abstract}

\section{Documentation and Installation}

You can download Gralog from \url{www.gralog.org} (Change this)

Gralog is written in Java and does not need special installation. Just
run the jar file by

[code, including where the jar file is]

or run Gralog directly from the source code by calling

[code: ./gradlew].

The documentation can be found in directory \texttt{doc/}. The main
manual file is \texttt{gralog.pdf}. This part is additionally in the
file \texttt{external.pdf}. [TODO: make a general manual, include this
text there.]

\input{console}



\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
