\documentclass{article}

\usepackage[T1]{fontenc}

\usepackage[margin=1.0in]{geometry}
\usepackage{longtable}

\usepackage{amsmath}

\newcounter{example}
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   \noindent \textit{Example~\theexample. #1} \rmfamily}{\medskip}

\usepackage{bbm}
\usepackage{booktabs}

\newcommand{\fabs}[1]{\mid {#1} \mid}

\newcommand{\bet}[1]{\llbracket {#1} \rrbracket^{\beta} }
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{makecell}

% \usepackage{mathabx}
\usepackage{amssymb,forest}

\usepackage{float}
\usepackage{MnSymbol}
\newlength\q
\newlength\smallCol
\newlength\argsLen
\setlength\q{\dimexpr .5\textwidth -2\tabcolsep}
\setlength\smallCol{\dimexpr .15\textwidth}
\setlength\argsLen{\dimexpr .2\textwidth}


\newcommand{\lto}{\mathbin{\to}}
\usepackage{booktabs}
\usepackage{enumitem} 
\usepackage{array}% for extended column definitions
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{tabto}
\newcommand{\ov}[2]{\ensuremath{\overset{\cdot {#2} \cdot}{#1}}}
\newcommand{\imp}{\rightarrow}

\usepackage{xstring}
\usepackage[german]{babel}
\usepackage[utf8]{inputenc}

\usepackage{lipsum}
\usepackage{listings}

\newcommand{\tcr}[1]{\textcolor{red}{#1}}

\definecolor{palegreen}{rgb}{0.9,1,0.9}
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=palegreen,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=5pt,
    arc=0pt,outer arc=0pt,
    after={\par\vspace{\baselineskip}\noindent},
  }
  \renewcommand{\arraystretch}{2}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{lightpink}{rgb}{1.0,0.9,0.9}
\definecolor{darkblue}{rgb}{0,0,0.4}

\usepackage{hyperref}

\hypersetup{colorlinks=true,linkcolor=darkblue,citecolor=darkblue}



\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\lstset{language=Python}

\title{Gralog Console Manual}

\author{Felix Herron\\\texttt{felix.herron@tu-berlin.de}
  \and Roman Rabinovich\\ \texttt{roman.rabinovich@tu-berlin.de}
\and Adrian Alic\\ \texttt{adrian.alic@campus.tu-berlin.de}}

\date{\today}

\begin{document}

\maketitle


\begin{abstract}
Gralog is a visual tool for working with graphs, logics, games,
transition systems and other structures based on undirected and
directed graphs. It can create, load, save and edit graphs in
various formats.

The key focus of Gralog is simplicity of use and a short time of
learning how to use it.

A special property of Gralog is that it helps the developer to write
programmes for graphs in any language capable of working with
pipes. Gralog visualises the run of the programme and can keep track
of values of user defined variables.

The interaction between Gralog and the external programme is
performed by a simple, but powerful protocol. In the first version
we implemented a library for Python that simplifies the interaction
and abstracts away the use of pipes. This paper describes the
protocol and the library, the External Programming Module (EPM). This
includes documentation of methods and classes pertaining to the
EPM and code examples for how to use these.
\end{abstract}

\section{Documentation and Installation}

You can download Gralog from \url{https://github.com/gralog/gralog}.

First, make sure that Java version at least 10 is installed on your
machine. (Currently, version 11 does not seem to work with Gralog.)

On Linux and Mac OS you can install it by

\begin{tcolorbox}
  cd..

  ./install-linux.sh
\end{tcolorbox}

This compiles Gralog in directory \texttt{~/gralog} (which is created
if necessary) or in the directory you give the script as a parameter:

\begin{tcolorbox}
  ./install-linux.sh /path/to/gralog
\end{tcolorbox}

Then a symbolic link to the script starting Gralog is created in
\texttt{/usr/bin}. For this, the installer asks the user for the admin
password. If you do not have it, just give three times a wrong
password: only the symbolic link part will be skipped.

Furthermore, the installer tries to install Python modules \emph{networkx} and
\emph{python-igraph} with \emph{pip}. If \emph{pip} is not installed,
it tries to install it. If Python is not installed, the installation
stops at this point (however, Python is installed by default on Linux
machines and on Macs). If on your machine by default, \emph{networkx}
and \emph{python-igraph} must be
installed to a directory you do not have writing rights for, the
installer asks for the \texttt{sudo} password.

You can skip the installation of the Python part giving the installer
parameter \texttt{-n} like this:

\begin{tcolorbox}
  ./install-linux.sh /path/to/gralog -n
\end{tcolorbox}
or
\begin{tcolorbox}
  ./install-linux.sh -n /path/to/gralog
\end{tcolorbox}

Finally, you can call the installer with parameter \texttt{-u}:

\begin{tcolorbox}
  ./install-linux.sh /path/to/gralog -u
\end{tcolorbox}
to let \emph{pip} try to install the modules locally. (This
corresponds to calling \texttt{pip install --user <module>}.)

On Windows Gralog is not tested yet. You can try to install it by
running

\begin{tcolorbox}
  gradlew.bat
\end{tcolorbox}
in the Gralog root directory. This compiles Gralog if necessary and
runs it. The \texttt{jar} file is
\texttt{./build/dist/gralog-fx.jar}. Similarly, on Linux and Mac OS
one can call
\begin{tcolorbox}
  ./gradlew
\end{tcolorbox}


On Windows and on newer Macs it is possible to call the jar file by
just clicking on it.

To use the python part on Windows, you have to install Python and the
libraries \emph{networkx} and \emph{python-igraph} yourself. Then copy
the file
\texttt{./gralog-fx/src/main/java/gralog/gralogfx/piping/scripts/Gralog.py}
to the directory with your Python script or somewhere where Python
will find it.


The documentation can be found in directory \texttt{doc/}. The main
manual file is \texttt{gralog.pdf}. This part is additionally in the
file \texttt{external.pdf}. [TODO: make a general manual, include this
text there.]


\input{console}
\input{external}




\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
